Stochastic Blockmodels for Relational Event Data

### 2012-05-29 docs/submission.tex
Small changes to paper and todos.

We allow the blocks to share information by placing a hierarchical prior on the collection of $\boldsymbol{\beta}_{k.l}$ where $\mu_p \sim N(0,1)$ and $\sigma_p^2 \sim \mbox{Gamma}(3,1)$ (TODO).

@@

\begin{itemize}
\item Kiel email: \cite{Ebel2002}
\item Enron email:
\item Tweets from Twitter.com occurring between from May 11, 2009 to January 26, 2012 that contained the hashtag \texttt{\#rstats}.\footnote{Will be made publicly available.}  This hashtag is used to denote messages pertaining to the R statistical computing environment and sometimes statistical discussion more generally.  We collect dyadic events by selecting tweets beginning with the \texttt{@} symbol (called a \emph{mention}), and mark the first mentioned user as the recipient.  Of 28337 total tweets in this time period, 3926 were directed events among a total of 1079 users.  We use the subset of 487 users who participated in more than one event, using a training set of 2000 events and a test set of 1330 events.
\item MIT Reality Mining: 
\end{itemize}

>>>>

We allow the blocks to share information by placing a hierarchical prior on the collection of $\boldsymbol{\beta}_{k.l}$ where $\mu_p \sim N(0,1)$ and $\sigma_p^2 \sim \mbox{Inv-Gamma}(3,1)$ (TODO).

@@

\begin{itemize}
\item Kiel email: \cite{Ebel2002}
\item Classrooms: \cite{McFarland2003}
\item Eckmann email: dyadic emails  \cite{Eckmann}
\item Enron email: dyadic emails between months [TODO], 3000 training and 1000 test events among 141 actors \cite{Enron}
\item Irvine: dyadic interactions among 401 actors each having more than 30 events,  \cite{Opsahl}
\item Tweets from Twitter.com occurring between from May 11, 2009 to January 26, 2012 that contained the hashtag \texttt{\#rstats}.\footnote{Will be made publicly available.}  This hashtag is used to denote messages pertaining to the R statistical computing environment and sometimes statistical discussion more generally.  We collect dyadic events by selecting tweets beginning with the \texttt{@} symbol (called a \emph{mention}), and mark the first mentioned user as the recipient.  Of 28337 total tweets in this time period, 3926 were directed events among a total of 1079 users.  We use the subset of 487 users who participated in more than one event, using a training set of 2000 events and a test set of 1330 events.
\item MIT Reality Mining:  \cite{MITreality}
\end{itemize}
